Improving \textsl{Gaia} parallax precision \\ with a data-driven model of stars

### 2018-03-05 paper/paper.tex
took out unmade figure

\begin{figure}
\centering
  \includegraphics[width=\textwidth]{posterior_odd.pdf}
\caption{Five example posterior PDFs over parallax using our method for more odd objects.
The upper left panel shows the position of each example data point in black, with its observed uncertainties, plotted over our prior represented by a mixture of Gaussians in green. In blue, we show the posterior expectation value and $1 \sigma$ uncertainties. 
We chose example points that lie outside the well populated portions of the \cmd to illustrate how our method works for rare \tgas objects. 
The remaining panels show the posterior PDF in blue, the prior PDF in green, and likelihood of the data in black.

Most stars have posterior PDFs (blue) that are only slightly more precise than the data (black), which is well represented in this random sampling of points.
Examples 1, 3, and 4 are not very effected by the prior (green), where good data is good data.
Examples 2 and 5 show a more precise posterior PDF compared with the likelihood.
Example 5 looks very similar to the prior PDF and exemplifies that our prior tends to have the largest effect on stars in the red giant branch.}
\label{fig:posterior}
\end{figure}

>>>>

%\begin{figure}
%\centering
%  \includegraphics[width=\textwidth]{posterior_odd.pdf}
%\caption{Five example posterior PDFs over parallax using our method for more odd objects.
%The upper left panel shows the position of each example data point in black, with its observed uncertainties, plotted over our prior represented by a mixture of Gaussians in green. In blue, we show the posterior expectation value and $1 \sigma$ uncertainties. 
%We chose example points that lie outside the well populated portions of the \cmd to illustrate how our method works for rare \tgas objects. 
%The remaining panels show the posterior PDF in blue, the prior PDF in green, and likelihood of the data in black.

%Most stars have posterior PDFs (blue) that are only slightly more precise than the data (black), which is well represented in this random sampling of points.
%Examples 1, 3, and 4 are not very effected by the prior (green), where good data is good data.
%Examples 2 and 5 show a more precise posterior PDF compared with the likelihood.
%Example 5 looks very similar to the prior PDF and exemplifies that our prior tends to have the largest effect on stars in the red giant branch.}
%\label{fig:posterior}
%\end{figure}
